Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-29 tex/ms.tex
discussion section start

\section{Discussion}
\label{sec:discussion}

\hogg{This section should include limitations of what we have done:  We didn't vary all available model parameters.  Our code is slow.  We don't permit time dependence to the censoring model.  Our noise model is naive at best.}

\hogg{This section should return to the detection point and the promise of that.}

\hogg{This section should NOT be a summary of the paper:  That lives in the abstract!}

>>>>

\section{Discussion}
\label{sec:discussion}
% This section should NOT be a summary of the paper:  That lives in the abstract!

We have shown that even the apparently ``null'' information that a
source was not detected can nonetheless be very informative, if the
generation of the nulls is \emph{modeled}.  This is true even in the
worst-case scenario that telescope sensitivity is not known or
derivable from the data or any meta data.  The inclusion of the null
data can have important impacts on parameter estimation; in particular
we have shown that it improves variable-star period and amplitude
estimation in heavily censored data sets.

Modeling the nulls brings great benefit.  It comes at cost, however:
Optimizing the marginalized likelihood (marginalizing out the latent
parameters related to the censoring) is computationally expensive.
It would be even more expensive if we had permitted all the
variables in our graphical model (\figurename~\ref{fig:pgm}) to vary.
Our method is far slower than the traditional method of ignoring the
nulls and performing linear least-squares fitting.

There are also various limitations to our approach, or aspects of what
we have presented here that could use improvement.  One is that our
noise model and censoring model were both extremely naive.  We
effectively assumed that the censoring process was related very
directly to signal-to-noise; this might not be the case in many
experiments.  In particular, sources are often missed because of
detector issues or chip gaps or other hardware-related reasons.  These
nulls could be modeled by our model without modification, but it would
be a ``bad fit'' to the true data-generating process.  A better model
might be a ``mixture'' model that permits some censoring to be caused
by more arbitrary processes.

We also assumed that the censoring process is constant in time.  This
is not true in general; in most optical systems the censoring would
depend (at least in part) on the weather, and the weather depends on
season and year.  It would be straightforward to add parameters that
permit the censoring to depend on season and year.

\hogg{This section should return to the detection point and the promise of that.  Can we give an example in ASAS of a de novo detection?}
